Formalization of Forcing in Isabelle/ZF

### 2020-05-04 src/document/root.tex
no reference to ZF-Constructible in abstract
Release notes in root.

\begin{abstract}
We formalize the theory of forcing in the set theory framework of
Isabelle/ZF. Under the assumption of the existence of a countable
transitive model of $\ZFC$, we construct a proper generic extension and show
that the latter also satisfies $\ZFC$. In doing so, we remodularized
Paulson's \verb|ZF-Constructibility| library.
\end{abstract}

@@

\section{Introduction}
This development is described in more detail in our papers
\cite{2018arXiv180705174G} (LSFA 2018), \cite{2019arXiv190103313G},
and \cite{2020arXiv200109715G} (IJCAR 2020).

>>>>

\begin{abstract}
We formalize the theory of forcing in the set theory framework of
Isabelle/ZF. Under the assumption of the existence of a countable
transitive model of $\ZFC$, we construct a proper generic extension and show
that the latter also satisfies $\ZFC$.
\end{abstract}

@@

\section{Introduction}
We formalize the theory of forcing. We work on top of the Isabelle/ZF
framework developed by \citet{DBLP:journals/jar/PaulsonG96}. Our
mechanization is described in more detail in our papers
\cite{2018arXiv180705174G} (LSFA 2018), \cite{2019arXiv190103313G},
and \cite{2020arXiv200109715G} (IJCAR 2020).

\subsection*{Release notes}
\label{sec:release-notes}

We have improved several aspects of our development before submitting
it to the AFP:
\begin{enumerate}
\item Our session \isatt{Forcing} depends on the new release of
  \isatt{ZF-Constructible}.
\item We streamlined the commands for synthesizing renames and formulas.
\item The command that synthesizes formulas produces the lemmas for
  them (the synthesized term is a formula and the equivalence between
  the satisfaction of the synthesized term and the relativized term).
\item Consistently use of structured proofs using Isar (except for one
  coming from a schematic goal command).
\end{enumerate}
